### 2017-12-12 master/paper.tex
Fix Title
Fix the size of figures

% Title
\thispagestyle{empty}
\begin{center}
\vspace*{5mm}
{\Huge {\bf Master's Thesis}}\\
\vspace{2cm}
% {\Large 題\hspace{8mm}目}\\
% \vspace{1cm}
\underline{\LARGE{Component-Based mruby Platform for IoT Devices}} \\
% \vspace{0.5cm}
% \underline{\LARGE{My Bachelor Thesis}} \\
\vspace{12mm}
{\large Supervisor}\\
\vspace{6mm}
\underline{\Large Professor Toshimitsu Ushio}\\
　\\
\underline{\Large Assistant Professor Takuya Azumi}\\
\vspace{8mm}
{\large By}\\
\vspace{6mm}
\underline{\Large Takuro Yamamoto}\\
\vspace{10mm}
{\Large February 7, 2018}\\
\vspace{14mm}
{\Large Division of Mathematical Science for Social Systems,\\Department of Systems Innovation,\\Graduate School of Engineering Science, Osaka University}\\
\end{center}
\clearpage
\setcounter{page}{0}
\pagenumbering{roman}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/SystemModel.pdf}
    \caption{System model of the proposed framework}
    \label{fig:SystemModel}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/component_diagram.pdf}
    \caption{Component Diagram}
    \label{fig:component}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TECSFlow.pdf}
    \caption{Development flow using TECS}
    \label{fig:TECSFlow}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mruby.pdf}
    \caption{mruby/RiteVM mechanism}
    \label{fig:mruby}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mrubyTECSbridge.pdf}
\caption{mruby-TECS bridge}
\label{fig:mrubyTECSbridge}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TINETHierarchyDiagram.pdf}
    \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
    \label{fig:TINETHierarchyDiagram}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/tMemoryAllocator.pdf}
    \caption{Component diagram of tMemoryAllocator}
    \label{fig:tMemoryAllocator}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/SendReceive.pdf}
    \caption{Differences between in/out and send/receive}
    \label{fig:SendReceive}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/DynamicConnection.pdf}
    \caption{Dynamic connection}
    \label{fig:DynamicConnection}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TLSF.pdf}
    \caption{TLSF Algorithm}
    \label{fig:TLSF}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/WithoutTECS.pdf}
    \caption{TLSF before componentization}
    \label{fig:WithoutTECS}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/WithTECS.pdf}
    \caption{TLSF after componentization}
    \label{fig:WithTECS}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/UseCase_mruby.pdf}
    \caption{Component description of RiteVM and TLSF+TECS}
    \label{fig:UseCase_mruby}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/UseCase_TINET.pdf}
    \caption{Fixed-size and TLSF memory allocator components}
    \label{fig:UseCase_TINET}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/EvaluationOfExecutionTime.pdf}
    \caption{Execution times of TINET and TINET+TECS}
    \label{fig:EvaluationOfExecutionTime}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
    \caption{Component diagrams for without/with dynamic connection}
    \label{fig:ComparisonOfDynamicConnection}
\end{figure}

>>>>

% Title
\thispagestyle{empty}
\begin{center}
\vspace*{5mm}
{\Huge {\bf Master's Thesis}}\\
\vspace{2cm}
% {\Large 題\hspace{8mm}目}\\
% \vspace{1cm}
\underline{\LARGE{Component-Based Software Development Framework}} \\
\vspace{0.5cm}
\underline{\LARGE{for Embedded IoT Devices}} \\
\vspace{12mm}
{\large Supervisor}\\
\vspace{6mm}
\underline{\Large Professor Toshimitsu Ushio}\\
　\\
\underline{\Large Assistant Professor Takuya Azumi}\\
\vspace{8mm}
{\large By}\\
\vspace{6mm}
\underline{\Large Takuro Yamamoto}\\
\vspace{10mm}
{\Large February 7, 2018}\\
\vspace{14mm}
{\Large Division of Mathematical Science for Social Systems,\\Department of Systems Innovation,\\Graduate School of Engineering Science, Osaka University}\\
\end{center}
\clearpage
\setcounter{page}{0}
\pagenumbering{roman}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/SystemModel.pdf}
    \caption{System model of the proposed framework}
    \label{fig:SystemModel}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/component_diagram.pdf}
    \caption{Component Diagram}
    \label{fig:component}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/TECSFlow.pdf}
    \caption{Development flow using TECS}
    \label{fig:TECSFlow}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/mruby.pdf}
    \caption{mruby/RiteVM mechanism}
    \label{fig:mruby}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/mrubyTECSbridge.pdf}
\caption{mruby-TECS bridge}
\label{fig:mrubyTECSbridge}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/TINETHierarchyDiagram.pdf}
    \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
    \label{fig:TINETHierarchyDiagram}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/tMemoryAllocator.pdf}
    \caption{Component diagram of tMemoryAllocator}
    \label{fig:tMemoryAllocator}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/SendReceive.pdf}
    \caption{Differences between in/out and send/receive}
    \label{fig:SendReceive}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/DynamicConnection.pdf}
    \caption{Dynamic connection}
    \label{fig:DynamicConnection}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/TLSF.pdf}
    \caption{TLSF Algorithm}
    \label{fig:TLSF}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/WithoutTECS.pdf}
    \caption{TLSF before componentization}
    \label{fig:WithoutTECS}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/WithTECS.pdf}
    \caption{TLSF after componentization}
    \label{fig:WithTECS}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/UseCase_mruby.pdf}
    \caption{Component description of RiteVM and TLSF+TECS}
    \label{fig:UseCase_mruby}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/UseCase_TINET.pdf}
    \caption{Fixed-size and TLSF memory allocator components}
    \label{fig:UseCase_TINET}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/EvaluationOfExecutionTime.pdf}
    \caption{Execution times of TINET and TINET+TECS}
    \label{fig:EvaluationOfExecutionTime}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
    \caption{Component diagrams for without/with dynamic connection}
    \label{fig:ComparisonOfDynamicConnection}
\end{figure}
